Figures

### 2019-06-19 figures/07_model-selection.Rmd
towards post hoc plots

```{r 07_model_selection, fig.height=3, echo=FALSE,eval=TRUE}
print("07_model_selection")
# setwd("figures")

@@

re_brms <- readRDS("../data/mcmc/re_brms.rds")
# lapply(re_brms, function(x) x$formula) 
signif_hu4_ids <- re_brms[[5]]$re_signif_ids # 5 is best tn model with re effects
signif_hu4 <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

gg_hu4_n <- ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2))

(gg_hu4_ndep <- ggplot() +
    geom_sf(data = hu4, aes(fill = hu4_nitrogen_atmospheric_deposition)) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()))

@@

plot_grid(
  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    # geom_point() +
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # geom_abline(slope = 1.55, intercept = -19.86, color = "red") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
  gplot_grid(gg_hu4_n, gg_hu4_ndep, ncol = 1),
  rel_heights = c(0.6, 1), labels = "AUTO", ncol = 2
)
```

```{r residual_dotplot, echo=FALSE}
suppressMessages(library(tidybayes))
suppressMessages(library(brms))

@@

```{r model_fitting, echo=FALSE, eval=TRUE}
library(brms)
library(tidybayes)
library(modelr)

@@

```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=TRUE}
# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_ag) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_ag, c(0.05, 0.5, 0.95)))))

@@

```{r signif_map, echo=FALSE, eval=TRUE}
ggplot() + 
  geom_sf(data = hu4) +
  geom_sf(data = hu4_signif, color = "red")
```

```{r model_summary, echo=FALSE, fig.height=3}

@@

```{r asdf, echo=FALSE}

>>>>

```{r 07_model_selection, fig.height=3, echo=FALSE, fig.width=6, eval=TRUE}
print("07_model_selection")
# setwd("figures")

@@

re_brms <- readRDS("../data/mcmc/re_brms.rds")
# lapply(re_brms, function(x) x$formula) 
fit_tn <- re_brms[[5]] # 5 is best tn model with re effects
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4 <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

# plotting
gg_hu4_n <- ggplot() +
    geom_sf(data = hu4, aes(fill = n_cat)) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) + 
    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
    guides(guide_legend(nrow = 2)) + 
  ggtitle("# of lakes")

gg_hu4_ndep <- ggplot() +
    geom_sf(data = hu4, aes(fill = hu4_nitrogen_atmospheric_deposition)) +
    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
    theme_minimal() + 
    theme(legend.position = "bottom", 
          axis.title = element_blank(), 
          legend.title = element_blank()) +
  ggtitle("N Deposition")

@@

gg_smooth <- ggplot(data = dt, 
                    aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
                color = "black", linetype = "dashed") +
    # geom_abline(slope = 1.55, intercept = -19.86, color = "red") +
    # scale_y_log10() + scale_x_log10() +
    theme(legend.position = "") +
    labs(x = "Ag. LULC (pct, NLCD 2011)", 
         y = "TP")  +
    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300))

plot_grid(gg_hu4_n, gg_hu4_ndep)
```

```{r prediction_lines, echo=FALSE, eval=TRUE}
# plot prediction lines
# corn vs tn

# hu4_signif$ZoneID
dt        <- readRDS("../data/dt_scaled.rds") 
names(dt) <- gsub("_", "v", names(dt))

hu4_id               <- signif_hu4_ids[1]
conditions           <- data.frame(hu4vzoneid = hu4_id)
rownames(conditions) <- hu4_id

me_zone <- marginal_effects(fit_tn, conditions = conditions, 
                            re_formula = NULL, method = "predict")

ran_ef <- as.data.frame(ranef(fit_tn)$hu4vzoneid) %>%
  mutate(zoneid = rownames(.)) %>%
  dplyr::filter(zoneid == hu4_id)

dplyr::filter(dt, hu4vzoneid %in% signif_hu4$ZoneID) %>%
  modelr::data_grid(corn = modelr::seq_range(corn, n = 101), 
                    maxdepth = modelr::seq_range(corn, n = 101), 
                    soilvorgvcarbon = modelr::seq_range(soilvorgvcarbon, n = 101), 
                    nitrogenvfertilizervuse = modelr::seq_range(nitrogenvfertilizervuse, n = 101), 
                    buffervcultivatedvcrops = modelr::seq_range(buffervcultivatedvcrops, n = 101), 
                    hu4vzoneid) %>%
  tidybayes::add_predicted_draws(fit_tn) %>%
  ggplot(aes(x = corn, y = tn)) +
  stat_lineribbon(aes(y = .prediction), 
                  .width = c(.99, .95, .8, .5), color = "#08519C") +
  geom_point(data = dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID), 
                                  size = 2) +
  scale_fill_brewer() +
  facet_wrap(~ hu4vzoneid)

```{r residual_dotplot, echo=FALSE, eval=FALSE}
suppressMessages(library(tidybayes))
suppressMessages(library(brms))

@@

```{r model_fitting, echo=FALSE, eval=FALSE}
library(brms)
library(tidybayes)
library(modelr)

@@

```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=FALSE}
# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_ag) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_ag, c(0.05, 0.5, 0.95)))))

@@

```{r signif_map, echo=FALSE, eval=FALSE}
ggplot() + 
  geom_sf(data = hu4) +
  geom_sf(data = hu4_signif, color = "red")
```

```{r model_summary, echo=FALSE, fig.height=3, eval=FALSE}

@@

```{r asdf, echo=FALSE, eval=FALSE}
